Fuzzy joins through deep learning

### 2018-07-28 paper2018/introduction.tex
edit networks a bit

In this paper, we propose a novel data driven approach to the problem of joining different representations of the same entity.  Our approach relies on building supervised deep learning models to automatically learn the correct set of transformations needed to compute the equality of two cell values.  For face recognition and person re-identification, siamese networks---in particular their `triplet' variants---have been used heavily; they are a natural fit for our problem too, since they train on both same and different data in comparisons, which is what we need for entity recognition.  We know of no work that has applied these techniques to the problem of fuzzy joins for entity names; furthermore, entity names have very different properties from faces, so we needed new techniques for selection of samples for training, and new loss functions.

@@

Our solution to the join problem involves building a system that performs deep metric learning.  That is, the specific function the network learns is to map input vectors corresponding to same entity closer in vector space compared to vectors that correspond to different entities.  This is typically achieved by training a so-called `triplet siamese network'.  At training, the network is given a triplet consisting of an `anchor' (e.g. \textit{Douglas Adams}), a positive element (e.g. \textit{Douglas Noel Adams}) and a negative element (e.g., John Adams), and it learns to produce a small distance estimate for the positive pair (close to 0), and a large distance estimate for the negative pair (above some margin $m$). A classification form of this function that simply learns whether two names belong to the same entity can be used to perform fuzzy joins, but then we would need a blocking strategy analogous to what has been used in the literature to identify the set of joinable pairs \cite{auto-join-joining-tables-leveraging-transformations}.

Our observation is that one can actually exploit what the siamese network produces to eliminate this blocking step altogether.  Specifically, the last hidden layer of the siamese network is effectively a `vector embedding' that contains the critical features needed for computing the distance estimate.  If such models are pre-built for a given entity type, we can then use the models to produce vector embeddings for all cell values in the two columns to be joined in a single linear pass, and index just the second column values in an approximate nearest neighbors index.  Then, for each cell value in the first column to be joined, querying the k-nearest neighbors should provide the set of values in the second column that can be joined.  Because approximate nearest neighbor algorithms have been applied successfully to billions of items \cite{JDH17}, this approach should scale just as well as join algorithms based on blocking, but has the added advantage that the blocking step is also data driven, and hence can adapt to different entity types very effectively.

>>>>

In this paper, we propose a novel data driven approach to the problem of joining different representations of the same entity.  Our approach relies on building supervised deep learning models to automatically learn the correct set of transformations needed to compute the equality of two cell values.  For face recognition and person re-identification, siamese networks---in particular their `triplet' variants---have been used successfully; they are a natural fit for our problem too, since they train on both same and different data in comparisons, which is what we need for entity recognition.  We know of no work that has applied these techniques to the problem of fuzzy joins for entity names; furthermore, entity names have very different properties from faces, so we needed new techniques for selection of samples for training, and new loss functions.

@@

Our solution to the join problem involves building a system that performs deep metric learning.  That is, the specific function the network learns is to map input vectors corresponding to same entity closer in vector space compared to vectors that correspond to different entities.  As in face recognition, we do this by training a `triplet siamese network'.  At training, the network is given a triplet consisting of an `anchor' (e.g. \textit{Douglas Adams}), a positive element (e.g. \textit{Douglas Noel Adams}) and a negative element (e.g., John Adams), and it learns to produce a small distance estimate for the positive pair (close to 0), and a large distance estimate for the negative pair (above some margin $m$). A classification form of this function that simply learns whether two names belong to the same entity can be used to perform fuzzy joins, but then we would need a blocking strategy analogous to what has been used in the literature to identify the set of joinable pairs \cite{auto-join-joining-tables-leveraging-transformations}.

Our observation is that one can actually exploit what the siamese network produces to eliminate this blocking step altogether.  Specifically, the last hidden layer (JD: output layer?) of the siamese network is effectively a `vector embedding' that contains the critical features needed for computing the distance estimate.  If such models are pre-built for a given entity type, we can then use the models to produce vector embeddings for all cell values in the two columns to be joined in a single linear pass, and index just the second column values in an approximate nearest neighbors index.  Then, for each cell value in the first column to be joined, querying the k-nearest neighbors should provide the set of values in the second column that can be joined.  Because approximate nearest neighbor algorithms have been applied successfully to billions of items \cite{JDH17}, this approach should scale just as well as join algorithms based on blocking, but has the added advantage that the blocking step is also data driven, and hence can adapt to different entity types very effectively.

### 2018-07-28 paper2018/siamese_networks.tex
adding angular loss
edit networks a bit

Section~\ref{acrhitecture} describes our overall network architecture for entity matching. Section~\ref{loss_functions} enumerates the different loss functions which have been used in prior work, and a new loss function which appears to do better in metric learning for entities.  Section~\ref{triplet_selection} describes a novel triplet selection mechanisms for entity matching.

@@

Figure~\ref{siamese_nets} illustrates overall network architecture we used to build a system for fuzzy joins.  Input vectors were computed assuming a maximum name length of 10 for each entity (i.e., no entity could have a name that spanned more than 10 words).  A 100 dimensional character embedding was computed for each `word' in the entity using pretrained embeddings \cite{hashimoto-jmt:2017:EMNLP2017}, which resulted in a 100 x 10 character encoding for each name used in a triplet.  As described earlier, in a triplet, each entity name (or \textit{anchor}) is paired with another name for the same entity (or \textit{positive}), and with a name for a completely different entity (or \textit{negative}).  The three input vectors from each triplet are fed to three identical networks that share the same weights.  Weight sharing ensures that the networks learn the same mapping function for any given input vector.  In our implementation, each of the three networks had 4 stacked layers of 128 unit Gated Recurrent Units (or GRUs) to capture the sequential nature of the input.

@@

The output of the last layer shown in the Figure~\ref{siamese_nets} as a dark gray layer produces a vector embedding for the inputs.  These are fed to two layers which compute a euclidean distance between the \textit{anchor} and the \textit{positive} elements of a triplet (\textit{positive distance}), and the \textit{anchor} and the \textit{negative} elements of a triplet (\textit{negative distance}).  Conceptually, there are two objectives in metric learning, one to minimize \textit{positive distances}, and the other to maximize \textit{negative distances}.  As described below, this dual objective is achieved by different loss functions in the literature.

@@

\subsubsection{Angular Loss}
Wang et al. \cite{DBLP:journals/corr/abs-1708-01682} define a novel angular loss function which is not based on pairwise distances, but rather is based on the angles of the triangle formed by the \textit{anchor}, \textit{positive} and the \textit{negative} triplet.  Conceptually, they point out that since the \textit{anchor} and the \textit{positive} pairs belong to the same class, the angle formed by the \textit{anchor}, \textit{negative}, and \textit{positive} elements should be as small as possible within that triangle.  Their loss function is an attempt to minimize this angle, as defined in the equation below.
\begin{equation}
\bf{x_{c}} = (\bf{x_{a}} + \bf{x_{c}}) / 2
\end{equation}
\begin{equation}
l_{triplet} = \left[[\bf{x_{a}} - \bf{x_{p}}\|^2 - 4 \tan^2 \alpha \|\bf{x_{n}} - \bf{x_{c}}\|^2 \right])_{+}
\end{equation}

>>>>

Section~\ref{architecture} describes our overall network architecture for entity matching.  Section~\ref{loss_functions} enumerates the different loss functions which have been used in prior work, and a new loss function which appears to do better in metric learning for entities.  Section~\ref{triplet_selection} describes a novel triplet selection mechanisms for entity matching.

@@

Figure~\ref{siamese_nets} illustrates overall network architecture we used to build a system for fuzzy joins.  Input is initially triples of a name (anchor), another name for the same entity (positive) and a name of another entity (negative).  For the network, input vectors are computed for each entity assuming a maximum name length of 10 for each entity (i.e., no entity could have a name that spanned more than 10 tokens).  A 100 dimensional character embedding was computed for each token in the entity using pretrained embeddings \cite{hashimoto-jmt:2017:EMNLP2017}, which resulted in a 100 x 10 character encoding for each name used in a triplet.  These three input vectors from each triplet are fed to three identical networks that share the same weights.  Weight sharing ensures that the networks learn the same mapping function for any given input vector.  In our implementation, each of the three networks had 4 stacked layers of 128 unit Gated Recurrent Units (or GRUs) to capture the sequential nature of the input.

@@

The output of the last layer shown in the Figure~\ref{siamese_nets} as a dark gray layer produces an output vector embedding for the inputs.  These are fed to two layers which compute a euclidean distance between the \textit{anchor} and the \textit{positive} elements of a triplet (\textit{positive distance}), and the \textit{anchor} and the \textit{negative} elements of a triplet (\textit{negative distance}).  Conceptually, there are two objectives in metric learning, one to minimize \textit{positive distances}, and the other to maximize \textit{negative distances}.  As described below, this dual objective is achieved by different loss functions in the literature.

@@

\subsubsection{Angular Loss}

\begin{figure}
\includegraphics[width=1\linewidth]{angular_loss}
\caption{Angular loss}
\label{angular_loss}
\end{figure}

Wang et al. \cite{DBLP:journals/corr/abs-1708-01682} define a novel angular loss function which is not based on pairwise distances, but rather is based on the angles of the triangle formed by the \textit{anchor}, \textit{positive} and the \textit{negative} triplet.  Conceptually, they point out that since the \textit{anchor} and the \textit{positive} pairs belong to the same class, the angle formed by the \textit{anchor}, \textit{negative}, and \textit{positive} elements should be as small as possible within that triangle.  Their loss function is an attempt to minimize this angle, as defined in the equation below.
\begin{equation}
\bf{x_{c}} = (\bf{x_{a}} + \bf{x_{c}}) / 2
\end{equation}
\begin{equation}
l_{triplet} = \left[[\bf{x_{a}} - \bf{x_{p}}\|^2 - 4 \tan^2 \alpha \|\bf{x_{n}} - \bf{x_{c}}\|^2 \right])_{+}
\end{equation}
